---
title: "R Notebook"
output: html_notebook
---

```{r}
europe_prod %>%
    filter(GDP_measure == "output_euros_per_hour") %>%
    group_by(industry) %>% 
    arrange(industry, desc(data)) %>%
        mutate(rank = row_number()) %>%
    arrange(desc(rank)) %>% 
    ggplot(aes(y =rank, x = NACE_code, fill = factor(country == "United Kingdom"), label = country)) +
    scale_fill_manual(name = "country", values = c("brown", "black")) +
    geom_tile(colour = "white", show.legend = FALSE) +
    geom_text(colour = "white", size = 4) +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    scale_y_reverse() +
    ylab("Low <--  Country Ranking - -> High")
```
```{r}
europe_prod %>%
    filter(GDP_measure == "output_euros_per_hour") %>%
    group_by(industry) %>% 
    arrange(industry, desc(data)) %>%
        mutate(rank = row_number()) %>%
    arrange(desc(rank)) %>%
    filter(country == "United Kingdom") %>% 
    ggplot(aes(y =rank, x = stringr::str_wrap(industry, 15), fill = factor(country == "United Kingdom"), label = country)) +
    scale_fill_manual(name = "country", values = c("black")) +
    geom_tile(colour = "white", show.legend = FALSE) +
    geom_text(colour = "white", size = 4) +
        theme(
            axis.text.x = element_text(vjust = 1, hjust = 0.5, size = 10, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    scale_y_reverse() +
    ylab("Low <--  Country Ranking - -> High")
```

```{r}

europe_prod %>%
    filter(GDP_measure == "output_euros_per_hour") %>%
    group_by(industry) %>% 
    arrange(industry, desc(data)) %>%
        mutate(rank = row_number()) %>%
    arrange(desc(rank)) %>%
    filter(country == "United Kingdom") %>% 
    ggplot(aes(y =rank, x = stringr::str_wrap(industry, 15), fill = rank, label = country)) +
    # scale_color_brewer(palette="RdYlGn") +
    geom_tile(colour = "white", show.legend = FALSE) +
    geom_text(colour = "white", size = 4) +
        theme(
            axis.text.x = element_text(vjust = 1, hjust = 0.5, size = 10, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    scale_y_reverse() +
    ylab("Low <--  Country Ranking - -> High")
```


European GDP measures to compare

```{r}
europe_prod <- read_csv("clean_data/EU_comparisons_by_sector.csv")

unique(europe_prod$GDP_measure)
```

Low productivity industries

# Identify and target industries with low productivity levels

```{r}
europe_prod %>%
    filter(GDP_measure == "output_euros_per_hour") %>%
    group_by(industry) %>% 
    arrange(industry, desc(data)) %>%
        mutate(rank = row_number()) %>%
    filter(country == "United Kingdom") %>% 
    arrange(desc(rank))
```
Low productivity growth industries

# Identify and target industries with low productivity levels

```{r}
europe_prod %>%
    filter(GDP_measure == "productivity_growth_pct") %>%
    group_by(industry) %>% 
    arrange(industry, desc(data)) %>%
        mutate(rank = row_number(),
               data = round(data,2)) %>%
    filter(country == "United Kingdom") %>% 
    arrange(desc(rank)) %>% 
    select(-GDP_measure, -NACE_code, -country)
```

## Proessional, scientific and technical

```{r}
library(ggpubr)

a <- europe_prod %>% 
    filter(
        industry == "Professional, scientific and technical activities; administrative and support service activities",
        GDP_measure == "output_euros_per_hour"
        ) %>% 
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == "United Kingdom") +
    geom_col(colour = "white") +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
        ylab("Output per hour (Euros)")

b <- europe_prod %>% 
    filter(
        industry == "Professional, scientific and technical activities; administrative and support service activities",
        GDP_measure == "productivity_growth_pct"
        ) %>% 
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == "United Kingdom") +
    geom_col(colour = "white") +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    ylab("Productivity growth %")

ggarrange(a, b) 

```


## Financial and insurance activities

```{r}

a <- europe_prod %>%
        filter(
        industry == "Public administration, defence, education, human health and social work activities",
        GDP_measure == "output_euros_per_hour"
        ) %>% 
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == "United Kingdom") +
    geom_col(colour = "white") +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    ylab("Output per hour (Euros)")

b <- europe_prod %>%
        filter(
        industry == "Public administration, defence, education, human health and social work activities",
        GDP_measure == "productivity_growth_pct"
        ) %>% 
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == "United Kingdom") +
    geom_col(colour = "white") +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    ylab("Output per hour (Euros)")

ggarrange(a, b)
```

## Public administration, defence, education, human health and social work activities
```{r}
# a <- 
    
    europe_prod %>%
    filter(
        industry == "Public administration, defence, education, human health and social work activities",
        GDP_measure == "output_euros_per_hour"
        ) %>%
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == c("United Kingdom")) +
    geom_col(colour = "white") +
        theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    ylab("Output per hour (Euros)")

europe_prod %>%
    filter(
        industry == "Public administration, defence, education, human health and social work activities",
        GDP_measure == "productivity_growth_pct"
        ) %>%
    ggplot() +
    aes(x = reorder(country, -data), y = data, fill = country == "United Kingdom") +
    theme(
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15),
        axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15, face = "bold"),
          legend.position = "none") +
    ylab("Output per hour (Euros)") 


```


What is the impact / significance of these laggards?

```{r}

```

