---
title: "The productivity problem"
output: html_notebook
---


# UK lags behind some other developed economies
```{r}
europe_prod %>% 
    group_by(industry) %>% 
    arrange(industry, desc(output_per_hour)) %>% 
        mutate(rank = row_number()) %>%
    filter(country == "United Kingdom") %>% 
    arrange(desc(rank))
```



# local business development and the wider economy are affected by productivity

```{r}

plot <- ggplot() + 
  geom_line(data=MS, aes(x=date, y=MSCI.World.PI, color='MS')) +
  geom_line(data=S, aes(x=date, y=SandP.TR, color='S')) +
  geom_line(data=BR, aes(x=date, y=MSCI.BRIC.PI, color='BR')) +
  geom_line(data=HF, aes(x=date, y=HFRX, color='HF')) +
  geom_line(data=LP, aes(x=date, y=LPX50.TR, color='LP')) +
  scale_color_manual(
      values = c(
           MS="red",
           S="blue",
          BR="green",
          HF="yellow",
          LP="violet" )) +
  labs(color="Indices") +
  xlab('Time') +
  ylab('Price')
plot

```




# Over the past decade, productivity has slowed down globally

Constant price GDP per hour worked - G7
```{r}

G7_prod_hist %>%
    ggplot() +
    aes(x = year, y = GDP_per_hour_worked, colour = country) +
    geom_line() +
    theme(legend.position = "bottom") 

# +
#     scale_color_manual(values=c(UK = "#999999"))


```







# “Productivity is commonly defined as a ratio between the output volume and the volume of inputs.

# Measures how efficiently production inputs are being used in an economy to produce a given level of output.

# Labour and capital inputs

# Identify and target industries with low productivity levels


# Example of initiatives within other nations to increase local productivity

# Main business question is generally: How can we improve productivity within Scotland and the UK overall?
 

# What factors can be improved to increase employee and/or business productivity across UK regions?



# Which industries are lagging behind in terms of productivity and how could they catch up?



# Can we predict overall UK productivity rates?



