---
title: "R Notebook"
output: html_notebook
---

Workforce jobs by region and industry (seasonally adjusted) excel file using Standard Industrial Classification (SIC) standards

• Jobs
• Hours




```{r}
reg_ind_prod <-
    read_csv("clean_data/UK_regional_productivity.csv")

reg_ind_prod %>%
distinct(industry)

reg_ind_prod %>%
filter(region == "UK")
```

```{r}
a <- reg_ind_prod %>%
    filter(industry == "Education and Health",
           info_type == "Output per hour worked",
           region == "UK") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
          legend.position = "bottom") +
    ggtitle("United Kingdom")+
    ylim(0,35) +    ylab("Output per hour worked")

b <- reg_ind_prod %>%
    filter(industry == "Education and Health",
           info_type == "Output per hour worked",
           region == "Scotland") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
              legend.position = "bottom"
            ) +
    ggtitle("Scotland") +
    ylim(0,35) +
    ylab("Output per hour worked")


ggarrange(a,b)
```
```{r}
a <- reg_ind_prod %>%
    filter(industry == "Education and Health",
           info_type == "Output per hour worked",
           region == "UK") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
          legend.position = "bottom") +
    ggtitle("United Kingdom")

b <- reg_ind_prod %>%
    filter(industry == "Education and Health",
           info_type == "Output per hour worked",
           region == "Scotland") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
              legend.position = "bottom"
            ) +
    ggtitle("Scotland")


ggarrange(a,b)
```
```{r}
a <- reg_ind_prod %>%
    filter(industry == "Financial Services",
           info_type == "Output per hour worked",
           region == "UK") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
          legend.position = "bottom") +
    ggtitle("United Kingdom")

b <- reg_ind_prod %>%
    filter(industry == "Financial Services",
           info_type == "Output per hour worked",
           region == "Scotland") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
              legend.position = "bottom"
            ) +
    ggtitle("Scotland")


ggarrange(a,b)
```
```{r}
a <- reg_ind_prod %>%
    filter(industry == "Financial Services",
           info_type == "Output per hour worked",
           region == "UK") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
          legend.position = "bottom") +
    ggtitle("United Kingdom")

b <- reg_ind_prod %>%
    filter(industry == "Financial Services",
           info_type == "Output per hour worked",
           region == "Scotland") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
              legend.position = "bottom"
            ) +
    ggtitle("Scotland")


ggarrange(a,b)
```

```{r}
reg_ind_prod %>%
    filter(industry == "Education and Health",
           info_type == "Output per hour worked",
           year == 2016) %>%
    ggplot() +
    aes(x = reorder(region, data), y = data, fill = region == "Scotland") +
    geom_col() +
    theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, face = "bold"),
            axis.title.y = element_blank(),
            axis.title.x = element_text(size = 15),
              legend.position = "none"
            ) +
    coord_flip() +
    ylab("Output per hour worked")
```


+
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
          legend.position = "bottom") +
    ggtitle("United Kingdom")

b <- reg_ind_prod %>%
    filter(industry == "Financial Services",
           info_type == "Output per hour worked",
           region == "Scotland") %>%
    group_by(subsector_letter) %>%
    arrange(subsector_letter) %>% 
    ggplot() +
    aes(x = year, y = data, group = subsector_letter, colour = subsector_letter) +
    geom_line() +
            theme(
            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0, size = 15, face = "bold"),
            axis.text.y = element_blank(),
            axis.title.x = element_blank(),
            axis.title.y = element_text(angle = 90, size = 15),
              legend.position = "bottom"
            ) +
    ggtitle("Scotland")
```


```{r}
reg %>%
    filter(year_month == max(year_month)) %>%
    group_by(industry) %>% 
    summarise(total_jobs = sum(jobs)) %>% 
    arrange(desc(total_jobs))


```





```{r}
reg_ind_prod %>% 
    filter(year == max(year),
           subsector_letter == "all_industries")
```

```{r}
reg_ind_prod %>% 
    filter(year == max(year),
           industry != "all_industries") %>%
    group_by(region, industry) %>% 
    summarise(industry_output_per_hour = sum(data)) %>% 
    arrange(industry_output_per_hour)
```

```{r}
reg_ind_prod %>% 
    filter(year == max(year),
           industry != "all_industries") %>%
    group_by(region, industry) %>% 
    summarise(industry_output_per_job = sum(data)) %>% 
    arrange(industry_output_per_job)
```

```{r}
reg_ind_prod %>%
    filter(industry == "financial_services") %>%
    group_by(year, region, industry) %>%
    summarise(output_per_job = sum(data)) %>% 
    ggplot() +
    aes(x = year, y = data, colour = region) +
    geom_line()
```

```{r}
scotland_output_per_job
```

```{r}
UK_regional_productivity_data <- read_csv("clean_data/UK_regional_productivity")
```

